Contextuality and the Born rule in fuzzy quantum theories

### 2017-05-10 prop_letter.tex
prop_letter.tex \paragraph{Gleason's Theorem} Add subscript in example.

\begin{example}\label{ex:three-dimensional-three-value}Given a three
dimensional Hilbert space with an orthonormal basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $.
Let $\mathscr{I}_{1}=\left\{ \necess,\imposs,\unknown\right\} $,
$\ket{\ps}=\left(\ket{0}+\ket{1}\right)/\sqrt{2}$, $\ket{\ps'}=\left(\ket{0}+\ket{2}\right)/\sqrt{2}$,
and
\begin{subequations}
\begin{eqnarray}
 &  & \begin{aligned}\imposs & =\bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})\\
 & =\bar{\mu}(\proj{\ps})=\bar{\mu}(\proj{\ps'})\textrm{ ,}
\end{aligned}
\\
 &  & \begin{aligned}\necess & =\bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}-\proj{0})\\
 & =\bar{\mu}(\mathbb{1}-\proj{\ps})=\bar{\mu}(\mathbb{1}-\proj{\ps'})\textrm{ ,}
\end{aligned}
\\
 &  & \unknown=\bar{\mu}(P)\qquad\textrm{otherwise.}
\end{eqnarray}
\end{subequations}
It is straightforward to verify that $\bar{\mu}$ is a convex quantum
IVPM.

Let $S_{1}=\left\{ \proj{0},\proj{\ps}\right\} $. Because $\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\imposs$,
we have $\mu_{\rho}^{\mathrm{B}}(\proj{0})=\mu_{\rho}^{\mathrm{B}}(\proj{\ps})=0$
for any mixed state~$\rho\in\coreBorn\left(\bar{\mu},S_{1}\right)$.
Hence, $\rho$ is actually $\ket{2}$, the only pure state orthogonal
to both $\ket{0}$ and $\ket{\ps}$. It is easy to verify $\proj{2}$
is actually in $\coreBorn\left(\bar{\mu},S_{1}\right)$.

Similarly, let $S_{2}=\left\{ \proj{0},\proj{\ps'}\right\} $. We
have $\coreBorn\left(\bar{\mu},S_{2}\right)=\left\{ \proj{1}\right\} $.
Therefore, 
\begin{equation}
\coreBorn\left(\bar{\mu},\events\right)\subseteq\coreBorn\left(\bar{\mu},S_{1}\right)\cap\coreBorn\left(\bar{\mu},S_{2}\right)=\emptyset
\end{equation}
and must be empty.
\end{example}

>>>>

\begin{example}\label{ex:three-dimensional-three-value}Given a three
dimensional Hilbert space with an orthonormal basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $.
Let $\mathscr{I}_{1}=\left\{ \necess,\imposs,\unknown\right\} $,
$\ket{\ps}=\left(\ket{0}+\ket{1}\right)/\sqrt{2}$, $\ket{\ps'}=\left(\ket{0}+\ket{2}\right)/\sqrt{2}$,
and
\begin{subequations}
\begin{eqnarray}
 &  & \begin{aligned}\imposs & =\bar{\mu}_{3}(\mathbb{0})=\bar{\mu}_{3}(\proj{0})\\
 & =\bar{\mu}_{3}(\proj{\ps})=\bar{\mu}_{3}(\proj{\ps'})\textrm{ ,}
\end{aligned}
\\
 &  & \begin{aligned}\necess & =\bar{\mu}_{3}(\mathbb{1})=\bar{\mu}_{3}(\mathbb{1}-\proj{0})\\
 & =\bar{\mu}_{3}(\mathbb{1}-\proj{\ps})=\bar{\mu}_{3}(\mathbb{1}-\proj{\ps'})\textrm{ ,}
\end{aligned}
\\
 &  & \unknown=\bar{\mu}_{3}(P)\qquad\textrm{otherwise.}
\end{eqnarray}
\end{subequations}
It is straightforward to verify that $\bar{\mu}_{3}$ is a convex
quantum IVPM.

Let $S_{1}=\left\{ \proj{0},\proj{\ps}\right\} $. Because $\bar{\mu}_{3}(\proj{0})=\bar{\mu}_{3}(\proj{\ps})=\imposs$,
we have $\mu_{\rho}^{\mathrm{B}}(\proj{0})=\mu_{\rho}^{\mathrm{B}}(\proj{\ps})=0$
for any mixed state~$\rho\in\coreBorn\left(\bar{\mu}_{3},S_{1}\right)$.
Hence, $\rho$ is actually $\ket{2}$, the only pure state orthogonal
to both $\ket{0}$ and $\ket{\ps}$. It is easy to verify $\proj{2}$
is actually in $\coreBorn\left(\bar{\mu}_{3},S_{1}\right)$.

Similarly, let $S_{2}=\left\{ \proj{0},\proj{\ps'}\right\} $. We
have $\coreBorn\left(\bar{\mu}_{3},S_{2}\right)=\left\{ \proj{1}\right\} $.
Therefore, 
\begin{equation}
\coreBorn\left(\bar{\mu}_{3},\events\right)\subseteq\coreBorn\left(\bar{\mu}_{3},S_{1}\right)\cap\coreBorn\left(\bar{\mu}_{3},S_{2}\right)=\emptyset
\end{equation}
and must be empty.\end{example}
